---
title: "p8105_hw6_msk2265"
author: "Mirah"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(broom)
```


```{r, include=FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())

```


The boostrap is helpful when you’d like to perform inference for a parameter / value / summary that doesn’t have an easy-to-write-down distribution in the usual repeated sampling framework. We’ll focus on a simple linear regression with tmax as the response with tmin and prcp as the predictors, and are interested in the distribution of two quantities estimated from these data:

r^2
log(β^1∗β^2)

Use 5000 bootstrap samples and, for each bootstrap sample, produce estimates of these two quantities.
```{r}
boot_sample = function(df) {
  sample_frac(df, replace = TRUE)
}
```

```{r}
boot_weather= weather_df %>% 
  modelr::bootstrap(n = 1000) |> 
  mutate(
    models = map(strap, \(df) lm(tmax ~ tmin + prcp, data = weather_df) ),
    results = map(models, broom::tidy)) |> 
  select(-strap, -models) |> 
  unnest(results) |> 
  group_by(term) 
```


```{r}
boot_straps = 
  tibble(strap_number = 1:1000) |> 
  mutate(
    strap_sample = map(strap_number, \(i) boot_sample(df = weather_df))
  )

boot_straps |> 
  slice(1:3) |> 
  mutate(strap_sample = map(strap_sample, arrange, tmin)) |> 
  pull(strap_sample)
```


```{r}
bootstrap_results_tidy = 
  boot_straps %>%  
  mutate(
    models = map(strap_sample, \(df) lm(tmax ~ tmin + prcp, data = weather_df)),
    tidy_results =map(models, tidy)) %>% 
  unnest(tidy_results)

bootstrap_results_glance = 
  boot_straps %>%  
  mutate(
    models = map(strap_sample, \(df) lm(tmax ~ tmin + prcp, data = weather_df)),
    glance_results =map(models, glance)) %>% 
  unnest(glance_results)
  
```

Plot the distribution of your estimates, and describe these in words. Using the 5000 bootstrap estimates, identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for r^2
 and log(β^0∗β^1)
 
. Note: broom::glance() is helpful for extracting r^2
 from a fitted regression, and broom::tidy() (with some additional wrangling) should help in computing log(β^1∗β^2)
.
